---
title: "QualityAlloys"
author: "Manish Grewal"
date: "26/07/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 8)
```

## Executive Summary

### Executive summary description here

## Load libraries
```{r loadlibs, warning=FALSE, message=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)

```

## Set working directory
```{r setwd}
setwd("C:/Users/manish.grewal/emdp/R/QualityAlloys")
```

## Load the dataset

```{r}
daily_visits <- read_excel("CU46-XLS-ENG.xls", sheet = "Daily Visits", skip = 4)

# Read the main worksheets from xls workbook  

weekly_visits <- read_excel("CU46-XLS-ENG.xls", sheet = "Weekly Visits", skip = 4)
financials <- read_excel("CU46-XLS-ENG.xls", sheet = "Financials", skip = 4)
lbs_sold <- read_excel("CU46-XLS-ENG.xls", sheet = "Lbs. Sold", skip = 4)

# and remove non alphabet characters from column headers (names)

names(weekly_visits) <- gsub("[^a-zA-Z]+", "", names(weekly_visits))
names(financials) <- gsub("[^a-zA-Z]+", "", names(financials))
names(lbs_sold) <- gsub("[^a-zA-Z]+", "", names(lbs_sold))

# gather columns into weekly_data
weekly_data <- data.frame(
  Week = weekly_visits$Week, 
  Visits = weekly_visits$Visits,
  UniqueVisits = weekly_visits$UniqueVisits, 
  Revenue = financials$Revenue, 
  Profit = financials$Profit, 
  LbsSold = financials$LbsSold)

# convert Week to ordered factored 
weekly_data$Week <- factor(weekly_data$Week, levels = weekly_data$Week)

idx_init <- which(levels(weekly_data$Week) == "Aug 24 - Aug 30")
idx_pre  <- which(levels(weekly_data$Week) == "Jan 18 - Jan 24")
idx_prom <- which(levels(weekly_data$Week) == "May 17 - May 23")
idx_post <- nrow(weekly_data)
weekly_data$Period <- c(rep("Initial Period", idx_init),
                        rep("Pre-promotion",  idx_pre - idx_init),
                        rep("promotion",      idx_prom - idx_pre),
                        rep("Post-promotion", idx_post - idx_prom))
View(weekly_data)
```


## 1. Column Charts 
### Initialize the common plot data
```{r}
p <- ggplot(weekly_data, aes(x = Week)) +
  scale_x_discrete(breaks = weekly_visits$Week[seq(1, nrow(weekly_visits), 2)]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### a. unique visits over time
```{r}
p +   geom_bar(aes(y = UniqueVisits), stat = "identity", fill = "blue", color = "black")
```

### b. revenue over time,
```{r}
p +   geom_bar(aes(y = Revenue), stat = "identity", fill = "blue", color = "black")
```

### c. profit over time

```{r}
p +   geom_bar(aes(y = Profit), stat = "identity", fill = "blue", color = "black")
```

### d. pounds sold over time.

```{r}
p +   geom_bar(aes(y = LbsSold), stat = "identity", fill = "blue", color = "black")
```

## 2. Summary by period

```{r}
by_period <- group_by(weekly_data, Period)
my_summ <- weekly_data %>% 
  group_by(Period) %>% 
  select(!Week) %>% 
  summarise(across(everything(), list(mean, median, sd, min, max)))

View(my_summ)
my_summ_init <- data.frame(as.list(my_summ[1,]), cols = 5)



### Summarize the data

```{r}
by_period <- group_by(weekly_data, Period)

summ <- data.frame()

x <- summarise(by_period, mean = mean(Visits), median = median(Visits), sd = sd(Visits), max = max(Visits), min = min(Visits))

str(x)
summ.Visits <- data.frame(t(summarise(by_period, mean = mean(Visits), median = median(Visits), sd = sd(Visits), max = max(Visits), min = min(Visits))))
View(summ.Visits)

summ.UniqueVisits <- summarise(by_period, mean = mean(UniqueVisits), median = median(UniqueVisits), sd = sd(UniqueVisits), max = max(UniqueVisits), min = min(UniqueVisits))

summ.Revenue <- summarise(by_period, mean = mean(Revenue), median = median(Revenue), sd = sd(Revenue), max = max(Revenue), min = min(Revenue))

summ.Profit <- summarise(by_period, mean = mean(Profit), median = median(Profit), sd = sd(Profit), max = max(Profit), min = min(Profit))

summ.LbsSold <- summarise(by_period, mean = mean(LbsSold), median = median(LbsSold), sd = sd(LbsSold), max = max(LbsSold), min = min(LbsSold))

summ_init <- summary(filter(weekly_data, Period == "Initial Period"))
View(summ_init)
```

### a. Initial period

```{r}
View(summ.Visits)
t(summ.Visits)

cbind(
  Visits =  filter(summ.Visits, Period == "Initial Period"),
  UniqueVisits = filter(summ.UniqueVisits, Period == "Initial Period")
)
```

