---
title: "QualityAlloys"
author: "Manish Grewal"
date: "26/07/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.width = 10, fig.height = 6.5)
```

## Executive Summary

### Executive summary description here

## Load libraries
```{r loadlibs, warning=FALSE, message=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)

```

## Set working directory
```{r setwd}
setwd("C:/Users/manish.grewal/emdp/R/QualityAlloys")
```

## Load the dataset

```{r}
daily_visits <- read_excel("CU46-XLS-ENG.xls", sheet = "Daily Visits", skip = 4)

# Read the main worksheets from xls workbook  

weekly_visits <- read_excel("CU46-XLS-ENG.xls", sheet = "Weekly Visits", skip = 4)
financials <- read_excel("CU46-XLS-ENG.xls", sheet = "Financials", skip = 4)
lbs_sold <- read_excel("CU46-XLS-ENG.xls", sheet = "Lbs. Sold", skip = 4)

# and remove non alphabet characters from column headers (names)

names(weekly_visits) <- gsub("[^a-zA-Z]+", "", names(weekly_visits))
names(financials) <- gsub("[^a-zA-Z]+", "", names(financials))
names(lbs_sold) <- gsub("[^a-zA-Z]+", "", names(lbs_sold))

# gather columns into weekly_data
weekly_data <- data.frame(
  Week = weekly_visits$Week, 
  UniqueVisits = weekly_visits$UniqueVisits, 
  Revenue = financials$Revenue, 
  Profit = financials$Profit, 
  LbsSold = financials$LbsSold)

# gather columns into weekly_data
weekly_data <- data.frame(
  Week = weekly_visits$Week, 
  Visits = weekly_visits$Visits,
  UniqueVisits = weekly_visits$UniqueVisits, 
  Revenue = financials$Revenue, 
  Profit = financials$Profit, 
  LbsSold = financials$LbsSold)

# convert Week to ordered factored 
weekly_data$Week <- factor(weekly_data$Week, levels = weekly_data$Week)

idx_init <- which(levels(weekly_data$Week) == "Aug 24 - Aug 30")
idx_pre  <- which(levels(weekly_data$Week) == "Jan 18 - Jan 24")
idx_prom <- which(levels(weekly_data$Week) == "May 17 - May 23")
idx_post <- nrow(weekly_data)
weekly_data$Period <- c(rep("Initial Period", idx_init),
                        rep("Pre-promotion",  idx_pre - idx_init),
                        rep("Promotion",      idx_prom - idx_pre),
                        rep("Post-promotion", idx_post - idx_prom))


weekly_data$period <- factor(weekly_data$Period, levels = c("Initial Period", "Pre-promotion", "Promotion", "Post-promotion"), ordered = TRUE)

```


## 1. Column Charts 
### Initialize the common plot data
```{r}
p <- ggplot(weekly_data, aes(x = Week)) +
  scale_x_discrete(breaks = weekly_visits$Week[seq(1, nrow(weekly_visits), 2)]) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### a. unique visits over time
```{r}
p +   geom_bar(aes(y = UniqueVisits), stat = "identity", fill = "blue", color = "black")
```

### b. revenue over time,
```{r}
p +   geom_bar(aes(y = Revenue), stat = "identity", fill = "blue", color = "black")
```

### c. profit over time

```{r}
p +   geom_bar(aes(y = Profit), stat = "identity", fill = "blue", color = "black")
```

### d. pounds sold over time.

```{r}
p +   geom_bar(aes(y = LbsSold), stat = "identity", fill = "blue", color = "black")
```

## 2. Summary by period

```{r}

by_period <- group_by(weekly_data, Period)

summ <- by_period %>% 
  select_if(is.numeric) %>% 
  summarise(across(everything(), list(mean, median, sd, min, max) 
                   #, .names = c("{col}.{fn}")
                   ))

summ_init <- as.data.frame(
  matrix(as.numeric(summ[1, 2:26]), nrow = 5), 
  row.names = c('mean', 'median', 'std. dev.', 'minimum', 'maximum'))
names(summ_init) <- names(by_period)[2:6]

summ_pre  <- as.data.frame(
  matrix(as.numeric(summ[3, 2:26]), nrow = 5),
  row.names = c('mean', 'median', 'std. dev.', 'minimum', 'maximum'))
names(summ_pre) <- names(by_period)[2:6]

summ_prom <- as.data.frame(
  matrix(as.numeric(summ[4, 2:26]), nrow = 5),
  row.names = c('mean', 'median', 'std. dev.', 'minimum', 'maximum'))
names(summ_prom) <- names(by_period)[2:6]

summ_post <- as.data.frame(
  matrix(as.numeric(summ[2, 2:26]), nrow = 5),
  row.names = c('mean', 'median', 'std. dev.', 'minimum', 'maximum'))
names(summ_post) <- names(by_period)[2:6]

```


### a. Summary table of Initial Period
```{r}
knitr::kable(summ_init, caption = "VISIT AND FINANCIAL SUMMARY MEASURES - INITIAL PERIOD")


```

### b. Summary table of Pre-promotion Period
```{r}
knitr::kable(summ_pre, caption = "VISIT AND FINANCIAL SUMMARY MEASURES - PRE PROMOTION PERIOD")


```

### c. Summary table of Promotion Period
```{r}
knitr::kable(summ_prom, caption = "VISIT AND FINANCIAL SUMMARY MEASURES - PROMOTION PERIOD")


```

### d. Summary table of Post-promotion Period
```{r}
knitr::kable(summ_post, caption = "VISIT AND FINANCIAL SUMMARY MEASURES - POST PROMOTION PERIOD")

```

## 3. Column chart of the means over the four periods

```{r}
p <- ggplot(summ, aes(x = Period))
```

### a. Mean Visits by Period
```{r}
p + geom_col(aes(y = Visits_1))
```

### b. Mean Unique Visits by Period
```{r}
# r, fig.show="hold", fig.width=3
p + geom_col(aes(y = UniqueVisits_1))
```

### c. Mean Revenue by Period
```{r}
p + geom_col(aes(y = Revenue_1))
```

### d. Mean Profit by Period
```{r}
p + geom_col(aes(y = Profit_1))
```

### e. Mean Lbs. Sold by Period
```{r}
p + geom_col(aes(y = LbsSold_1), stat = "identity")
```

## 4. Summary of findings thus far

#### Average visits and average unique visits have shown a marked increase in promotion period. However, profit, revenue and lbs. sold show a steady declining trend over the four periods. This suggests that the website promotion did not have a positive effect on financials.

## 5. Revenue and Lbs. Sold

### a. Scatter plot Revenue and Lbs. Sold

```{r}
ggplot(weekly_data, aes(LbsSold, Revenue)) +
  geom_point() +
  geom_smooth()
```

### b. Coefficient of Correlation

```{r}

cor_coef <- cor(weekly_data$LbsSold, weekly_data$Revenue, method = "pearson")
cor_coef
```

## 6. Revenue and Visits

### a. Scatter plot Revenue and Visits

```{r}
ggplot(weekly_data, aes(Visits, Revenue)) +
  geom_point() +
  geom_smooth()

```

## 7. Summary of results
The scatterplot mirrors the earlier observations from Q4. Revenue does not increase or decrease with visits

## 8. Modeling data

### a. Summary of Lbs. Sold data per week from January 3, 2005, through the week of July 19, 2010.

```{r}

lbs_sold_mean <- mean(lbs_sold$LbsSold)
lbs_sold_sd   <- sd(lbs_sold$LbsSold)
paste("Mean:",      mean(lbs_sold$LbsSold))
paste("Median:",    median(lbs_sold$LbsSold))
paste("Std. Dev.:", sd(lbs_sold$LbsSold))
paste("Minimum:",   min(lbs_sold$LbsSold))
paste("Maximum:",   max(lbs_sold$LbsSold))

```

### b. Histogram of the pounds of material sold data.

```{r}
ggplot(lbs_sold, aes(LbsSold), color = "blue") +
  geom_histogram()
```

### c. Histogram appears bell shaped with few outliers on the right side. Also, mean is greater than median, so the data is right skewed.

### d. Empirical rule

```{r}
emp_rule <- data.frame(
  "Interval" = c("mean ?? 1 std. dev.", "mean ?? 2 std. dev.", "mean ?? 3 std. dev. 99%"),
  "TheoreticalPctOfData" = c(68, 95, 99)
  )

emp_rule$TheoreticalNoOfObs <- emp_rule$TheoreticalPctOfData * nrow(lbs_sold) / 100
emp_rule$ActualNoOfObs <- c(0)
emp_rule$ActualNoOfObs <- c(
  nrow(filter(lbs_sold, 
              LbsSold > lbs_sold_mean - lbs_sold_sd, 
              LbsSold < lbs_sold_mean + lbs_sold_sd)),
  nrow(filter(lbs_sold, 
              LbsSold > lbs_sold_mean - 2*lbs_sold_sd, 
              LbsSold < lbs_sold_mean + 2*lbs_sold_sd)),
  nrow(filter(lbs_sold, 
              LbsSold > lbs_sold_mean - 3*lbs_sold_sd, 
              LbsSold < lbs_sold_mean + 3*lbs_sold_sd)))
knir::kable(emp_rule)
```




### e. 
