---
title: "Darla"
author: "Manish Grewal"
date: "15/05/2021"
output:
  
  html_document: 
    theme: cerulean
    toc: true
    toc_depth: 3
  word_document: default
  pdf_document: default
  always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 16)
options(scipen=10000)
st <- proc.time()
```

<style type="text/css">
 .main-container {
   max-width: 1800px;
   margin-left: auto;
   margin-right: auto;
 }
</style>


```{r libs}
library(readxl)
library(ggplot2)
library(dplyr)
library(kableExtra)
library(DT)

#options(knitr.table.format = "html") 
#library(esquisse)
```

```{r load_data, eval=FALSE}
setwd("C:/Users/manish.grewal/git-emdp/emdp/darla")

inactive_sites <- read_excel("RFC-2373-inactive-site-list.xlsx")

events_critical <-
  c(
    "welcomeEmail",
    "reminderEmail",
    "driveAssignment",
    "eptest1",
    "drive assignment retry",
    "reviewerReminderEmail",
    "reminder email series",
    "campaignDailyMailDelivery",
    "thankYouEmail",
    "campaignHourlyMailDelivery",
    "correctSubmissionEmail"
  )
events_secondary <-
  c(
    "reportDeliver",
    "driveAssignmentValidate",
    "eptest2",
    "notifyNearStart",
    "notifyNearDue",
    "notifyNearClose",
    "notifyClosed",
    "validateAnnouncementRecipients",
    "validateReminderRecipients",
    "bulkload poll",
    "reportNow",
    "driveAssignmentValidateReport",
    "validateReviewerReminderRecipients",
    "validateCorrectSubmissionRecipients",
    "reminderEmailRetry",
    "welcomeEmailRetry",
    "reviewerReminderEmailRetry",
    "correctSubmissionEmailRetry",
    "validateAnnouncementRecipientsUseAssignmentRules",
    "validateReminderRecipientsUseAssignmentRules",
    "VariableWelcomeEmailRetry",
    "VariableReminderEmailRetry",
    "VariableReviewerReminderEmailRetry",
    "VariableCorrectSubmissionReminderEmailRetry",
    "FailedEmailDeliveryReport",
    "CumulativeEmailRetry",
    "supervisorEmail"
  )
events_tertiary <-
  c(
    "lyris poll",
    "lyris gc",
    "monitor",
    "dailyAdminEmail",
    "unitTest",
    "dailyLogRotation",
    "computeCampaignProgress",
    "computeLicenseReports",
    "eptest3",
    "ContractModulesExceeded"
  )

dat1 <- read.csv("eventmetrics1.csv")
dat2 <- read.csv("eventmetrics2.csv")

dat <- rbind(dat1, dat2)
dat1 <- dat2 <- NULL

# drop unused cols
dat <-
  dat[, c(
    "id",
    "lcecSiteId",
    "processorId",
    "campaignId",
    "eventTypeEnum",
    "scheduledFor",
    "executedAt",
    "milliseconds"
  )]

###############
# Fix date cols
###############
# Add :00 if seconds part missing
dat$executedAt <-
  gsub("^(.{10} [0-9][0-9]:[0-9][0-9])$", "\\1:00", dat$executedAt)
dat$executedAt <-
  strptime(dat$executedAt, format = "%d-%m-%Y %H:%M:%S", tz = "America/Los_Angeles")

# Add :00 if seconds part missing
dat$scheduledFor <-
  gsub("^(.{10} [0-9][0-9]:[0-9][0-9])$", "\\1:00", dat$scheduledFor)
dat$scheduledFor <-
  strptime(dat$scheduledFor, format = "%d-%m-%Y %H:%M:%S", tz = "America/Los_Angeles")
#######################


## add index col
dat <- dat %>%
  mutate(index1 = row.names(dat), .before = 1)

#######################
# add queue_type col
#######################
dat$queue_type <- case_when(
  dat$eventTypeEnum %in% events_critical ~ "critical",
  dat$eventTypeEnum %in% events_secondary ~ "secondary",
  dat$eventTypeEnum %in% events_tertiary ~ "tertiary"
)

# Queue changed for this job from secondary to tertiary on 18th April
dat$queue_type[dat$eventTypeEnum == "driveAssignmentValidateReport" &
                 dat$scheduledFor >= "2021-04-18 12:00:00"] <- "tertiary"
#######################

dat$lcecSiteId <- as.factor(dat$lcecSiteId)
#dat$eventTypeEnum <- as.factor(dat$eventTypeEnum)
dat$queue_type <- as.factor(dat$queue_type)
dat$secs <- dat$milliseconds / 1000

dat <- filter(dat, processorId != -1)
dat$processorId <- as.factor(as.character(dat$processorId))

dat$delay_min <- (as.numeric(dat$executedAt - dat$scheduledFor)) / 60
dat$sched_date <- format(dat$scheduledFor, format = '%Y/%m/%d')
dat$sched_time <- format(dat$scheduledFor, format = '%H:%M:%S')
#dat$sched_daydate <- format(dat$scheduledFor, format = '%Y/%m/%d %a')
dat$sched_day <- format(dat$scheduledFor, format = '%a')
dat$sched_day <- factor(
  dat$sched_day,
  ordered = TRUE,
  levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
)
dat$sched_time_30 <- paste0(
  substr(dat$sched_time, 1, 3),
  ifelse(as.integer(substr(dat$sched_time, 4, 5)) >= 30, "30", "00")
  )

dat$active <- ifelse(dat$lcecSiteId %in% inactive_sites$Site, "inactive", "active")

idx_rel1 <- which(dat$scheduledFor == "2021/04/18 12:00:00")[1]
idx_rel2 <- which(dat$scheduledFor == "2021/05/06 09:00:00")[1]

dat$period <- c(
  rep("Before", idx_rel1),
  rep("Release1", idx_rel2 - idx_rel1),
  rep("Release2", nrow(dat) - idx_rel2)
)

```

```{r}
dat = readRDS("dat.RDS")
```


```{r eval=FALSE}
#kbl(summary(dat[,-1])) %>%
#  kable_paper("hover", full_width = T)
```


```{r}

# The palette with grey:
cbp1 <- c("#999999", "#D55E00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#E69F00", "#CC79A7")

plot_by_date <- function(x, y, desc) {
  
  what <- gsub("_", " ", y)
  title <- paste("By date:", what, "(", desc, ")")
  
  print(title)
  
  idx_rel1 <- which(x$sched_date == "2021/04/18")
  idx_rel2 <- which(x$sched_date == "2021/05/06")
  
  p <- x %>%
    ggplot(aes(x = sched_date)) +
    geom_col(aes_string(y = y, fill = "sched_day")) +
    theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) +
    #scale_fill_manual(values = cbp1) +
    xlab("Date") +
    ylab(what) +
    ggtitle(title) +
    geom_vline(aes(xintercept = c(idx_rel1), color="Rel1"), size=1, linetype="dashed") +
    geom_vline(aes(xintercept = c(idx_rel2), color="Rel2"), size=1, linetype="dashed") +
    scale_color_manual(name = "Release", values = c(Rel1 = "blue", Rel2 = "black")) +
    scale_x_discrete(breaks = x$sched_date[seq(1, nrow(x), 2)])

  print(p)
}

plot_by_date_all <- function(x, desc) {
  plot_by_date(x, "average_delay_minutes", desc)
  plot_by_date(x, "max_delay_minutes", desc)
  plot_by_date(x, "average_execution_minutes", desc)
  plot_by_date(x, "total_delay_minutes", desc)
  plot_by_date(x, "total_execution_minutes", desc)
  plot_by_date(x, "count", desc)
}

plot_by_period <- function(x, queue) {
  title <- paste("Impact of releases", queue, "queue")
  print(title)

  p <- x %>%
    filter(queue_type == queue) %>%
    ggplot(aes(x = sched_day, y = average_delay_minutes)) +
    geom_col(aes(fill = period), position = "dodge") +
    facet_wrap( ~ queue_type) +
    xlab("Average delay minutes") +
    ylab("Day") +
    ggtitle(title) +
    scale_fill_brewer(palette = "Dark2")
  print(p)
}
```

# IMPACT OF RELEASES

## SUMMARY - IMPACT OF RELEASES BY QUEUE TYPE

```{r}
by_period <- group_by(dat, period, queue_type)

summ_period <- by_period %>%
  summarise(average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min),
            count = n())
  

names(summ_period) <- gsub("_minutes", "", names(summ_period))
# knitr::kable(summ_period, caption = "IMPACT OF RELEASES (minutes)") %>%
#   kable_paper("hover", full_width = T)

datatable(summ_period, filter = 'top', caption = "IMPACT OF RELEASES (minutes)")
```

## AVERAGE DELAY - IMPACT OF RELEASES BY QUEUE TYPE AND DAY OF WEEK

```{r}
by_period <- dat %>%
  #filter(!sched_date %in% c("2021/02/28", "2021/04/04")) %>%
  group_by(period, queue_type, sched_day)
  

summ_period <- by_period %>%
  summarise(average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min),
            count = n())

title <- paste("Impact of releases")
print(title)
  
summ_period %>%
  ggplot(aes(x = sched_day, y = average_delay_minutes)) +
  geom_col(aes(fill = period), position = "dodge") +
  facet_wrap(~queue_type) +
  xlab("Average delay minutes") +
  ylab("Day") +
  ggtitle(title) +
  scale_fill_brewer(palette = "Dark2")

  
plot_by_period(summ_period, "critical")
plot_by_period(summ_period, "secondary")
plot_by_period(summ_period, "tertiary")


names(summ_period) <- gsub("_minutes", "", names(summ_period))
# knitr::kable(summ_period, caption = "IMPACT OF RELEASES (minutes)") %>%
#   kable_paper("hover", full_width = T)
```

## SUMMARY - IMPACT OF RELEASES BY QUEUE TYPE AND DAY OF WEEK

```{r}
# summ_period %>%
#   ggplot(aes(x = sched_day, y = average_delay_minutes)) +
#   geom_col(aes(fill = period), position = "dodge")

```

```{r}
datatable(summ_period, filter = 'top', caption = "IMPACT OF RELEASES (minutes)")
```

# BY TIME OF DAY

```{r}
by_queue_day_time <- dat %>%
  group_by(queue_type, sched_day, sched_time_30)

summ1 <- by_queue_day_time %>%
  summarise(average_delay_minutes = mean(delay_min), count = n())
```

## COUNT OF JOBS BY TIME OF DAY

```{r fig.height=8}
title <- "Count of jobs by time of day"
print(title)
summ1 %>%
  ggplot(aes(x = sched_time_30, y = count)) +
  geom_col(aes(fill = sched_day), position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) +
  facet_wrap( ~ queue_type, ncol = 1) +
  xlab("Scheduled Time") +
  ggtitle(title)

```


## AVERAGE DELAY BY TIME OF DAY

```{r fig.height=8}
title <- "Average delay by time of day"
print(title)
summ1 %>%
  ggplot(aes(x = sched_time_30, y = average_delay_minutes)) +
  geom_col(aes(fill = sched_day), position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) +
  facet_wrap( ~ queue_type, ncol = 1) +
  xlab("Scheduled Time") +
  ylab("average delay minutes") +
  ggtitle(title)

```

## IMPACT OF RELEASES BY TIME OF DAY - AVERAGE DELAY

```{r}
by_period_time <- dat %>%
  group_by(period, queue_type, sched_day, sched_time_30)

summ <- by_period_time %>%
  summarise(count = n(), average_delay_minutes = mean(delay_min))
```


```{r fig.height=9}
title <- "Impact of releases - Average delay by time of day"
print(title)
summ %>%
  ggplot(aes(x = sched_time_30, y = average_delay_minutes)) +
  geom_col(aes(fill = sched_day), position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) +
  scale_x_discrete(breaks = unique(summ$sched_time_30)[seq(1, length(summ$sched_time_30), 2)]) +
  facet_grid(period ~ queue_type) +
  xlab("Scheduled Time") +
  ggtitle(title)
```

## IMPACT OF RELEASES BY TIME OF DAY - AVERAGE DELAY - SECONDARY QUEUE


```{r fig.height=8}
title <- "Impact of releases - Average delay by time of day - secondary queue"
print(title)
summ %>%
  filter(queue_type == "secondary") %>%
  ggplot(aes(x = sched_time_30, y = average_delay_minutes)) +
  geom_col(aes(fill = sched_day), position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) +
  scale_x_discrete(breaks = unique(summ$sched_time_30)[seq(1, length(summ$sched_time_30), 1)]) +
  facet_wrap(period ~ queue_type, ncol = 1) +
  xlab("Scheduled Time") +
  ggtitle(title)
```

## SUMMARY - IMPACT OF RELEASES BY TIME OF DAY

```{r}
datatable(summ_period, filter = 'top', caption = "IMPACT OF RELEASES (minutes)")
```


# BY DATE


```{r by_date_main}
by_date <- dat %>%
  group_by(sched_date, sched_day)

summ <- summarise(by_date, average_delay_minutes = mean(delay_min),
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60),
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min),
            count = n())

```

## BY DATE - OVERALL

```{r}
plot_by_date_all(summ, "All Queues")
```

#### Delay Outliers

Huge delays on 2/28 and 4/4 are due to Sunday maintenance activities during which the queues were paused for longer duration. The data for these two dates are excluded from further analysis.

## BY DATE - OVERALL - without outliers

```{r}
by_date <- dat %>%
  filter(!sched_date %in% c("2021/02/28", "2021/04/04")) %>%
  group_by(sched_date, sched_day)

summ <- summarise(by_date,average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min), 
            count = n())
```


```{r}
plot_by_date_all(summ, "All Queues - 2 dates excluded")
```


## BY DATE - BY QUEUE


```{r}

summ_cri <- by_date %>%
  filter(queue_type == "critical") %>%
  summarise(average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min), 
            count = n())

summ_sec <- by_date %>%
  filter(queue_type == "secondary") %>%
  summarise(average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min), 
            count = n())


summ_ter <- by_date %>%
  filter(queue_type == "tertiary") %>%
  summarise(average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min),
            count = n())
```

### BY DATE (Critical queue)


```{r}
plot_by_date_all(summ_cri, "Critical Queue")
```

### BY DATE (Secondary queue)


```{r}
plot_by_date_all(summ_sec, "Secondary Queue")
```

### BY DATE (Tertiary queue)

```{r}

summ_ter <- summ_ter %>%
  filter(!sched_date %in% c("2021/05/02", "2021/04/03"))

plot_by_date_all(summ_ter, "Tertiary Queue")


```

## BY DATE (Secondary queue) - reportNow and reportDeliver

```{r}
summ <- by_date %>%
  filter(eventTypeEnum %in% c("reportNow", "reportDeliver")) %>%
  summarise(average_delay_minutes = mean(delay_min), 
            total_delay_minutes = sum(delay_min),
            average_execution_minutes = mean(secs/60), 
            total_execution_minutes = sum(secs/60),
            max_delay_minutes = max(delay_min),
            count = n())
```


```{r}
plot_by_date_all(summ, "Secondary Queue - Reports")
```





# BY PARTNER

## Jobs by partner (count > 2000)
```{r}


by_site <- group_by(dat, lcecSiteId, active)
summ <- summarise(by_site, count = n())
#View(summ)
```

```{r}

summ %>%
  filter(count > 2000) %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(x = reorder(lcecSiteId, -count), y = count), color = "red") +
  theme(axis.text.x = element_text(angle = 90)) 
  
```

## Jobs by partner (secondary)

```{r}


by_site_queue <- group_by(dat, lcecSiteId, queue_type)
summ <- summarise(by_site_queue, count = n())
#View(summ)
```
```{r}

summ %>%
  filter(queue_type == "secondary", count > 300) %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(x = reorder(lcecSiteId, -count), y = count, fill = queue_type)) +
  theme(axis.text.x = element_text(angle = 45)) 
  
```

# BY EVENT TYPE

## Jobs by eventType, queue_type

```{r}
by_event_type <- group_by(dat, eventTypeEnum, queue_type)
summ <- summarise(by_event_type, count = n(), avg_secs = mean(secs), total_secs =sum(secs))
summ %>%
  #filter(ct > 2000) %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(y = reorder(eventTypeEnum, -count), x = count, fill = queue_type)) 
  #facet_wrap(~queue_type) +
  # + theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7))
```

## Jobs by eventType, queue_type (log scale)

```{r}
by_event_type <- group_by(dat, eventTypeEnum, queue_type)
summ <- summarise(by_event_type, count = n())
summ <- summarise(by_event_type, count = n(), avg_secs = mean(secs), total_secs =sum(secs))
summ %>%
  #filter(ct > 2000) %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(y = reorder(eventTypeEnum, -count), x = log10(count), fill = queue_type)) +
  #facet_wrap(~queue_type) +
  theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) 

```


## Average execution time by event type

```{r}
summ %>%
  #filter(ct > 2000) %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(y = reorder(eventTypeEnum, -count), x = avg_secs, fill = queue_type)) 
  #facet_wrap(~queue_type) +
  # + theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) 

```

## Average execution time by event type (secondary)

```{r}
summ %>%
  filter(queue_type == "secondary") %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(y = reorder(eventTypeEnum, -avg_secs), x = avg_secs, fill = queue_type))
  #facet_wrap(~queue_type) +
  # + theme(axis.text.x = element_text(angle = 90, size = 11, vjust = 0.7)) 

```


```{r}
proc.time() - st
knitr::knit_exit() 
```


```{r}
### cut into bins

d1 <- dat %>% filter(secs > 1000)
d1 <- dat %>%
  filter(queue_type == "secondary" & secs > 10 & secs < 1000) 

ggplot(d1, aes(x = round(secs))) + geom_histogram(binwidth = 10, fill = "red", color = "black")

```

