---
title: "Churn"
author: "Manish Grewal"
date: "29/07/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4)
```

## Load the libraries
```{r load_libs, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)

```

## Set working directory
```{r setwd}
setwd("C:/Users/manish.grewal/emdp/R/churn")
```

## Load the dataset
```{r load_dataset}
churn <- read.csv("churn.csv")
```

# Use the churn data set, and complete the following exercises:

## 1. Explore whether there are missing values for any of the variables.

```{r}
any( is.na( churn ) )
```

There are no missing values. `summary(churn)` also does not show any `NA` values.

```{r include=FALSE}
#summ <- data.frame(do.call(rbind, lapply(churn, summary)))
#summ$Mean <- gsub("^(\\d+\\.\\d\\d\\d)\\d+", "\\1", summ$Mean)
#knitr::kable(summ, digits = 3)
```

```{r fig.width=10, fig.height=10}
churn$Area.Code = as.character(churn$Area.Code)
churn %>% 
  select_if(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram() +
    labs(title = "Histogram of numeric variables") +
    theme_bw()
```

```{r}
churn %>% 
  select_if(is.character) %>% 
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") + 
    geom_histogram(stat = "count") +
    labs(title = "Histogram of character variables") +
    theme_bw()

```


Histogram of Area.Code shows only 3 different values, which may require further exploration as the same 3 area codes are appearing for different states.

VMail.Message also shows a high number of records with 0 value. 

## 2. Use a graph to visually determine whether there are any outliers among the number of calls to customer service.

```{r}
ggplot(churn) +
  aes(x = "", y = CustServ.Calls) +
  geom_boxplot(fill = "blue") +
  scale_y_continuous(n.breaks = 10) +
  theme_bw()
```

The box plot shows the values 4 to 9 are outliers among the number of calls to customer service.

## 3. Identify the range of customer service calls that should be considered outliers, using:

### a. the Z-score method;  

```{r}
churn$CustServ.Calls_zscore <- (churn$CustServ.Calls - mean(churn$CustServ.Calls)) / sd(churn$CustServ.Calls) 

outliers <- churn %>%
  filter(CustServ.Calls_zscore < -3 |
         CustServ.Calls_zscore > 3) %>% 
  select(CustServ.Calls, CustServ.Calls_zscore)

sort(unique(outliers$CustServ.Calls))
```

Outliers using the z-score method are the customers who made the following number of calls:  
**`r sort(unique(outliers$CustServ.Calls))`**

### b. the IQR method  

```{r}
summary(churn$CustServ.Calls)
Q1 <- as.numeric(quantile(churn$CustServ.Calls, 0.25)); Q1
Q3 <- as.numeric(quantile(churn$CustServ.Calls, 0.75)); Q3
IQR <- Q3 - Q1; IQR

outliers <- churn %>%
  filter(CustServ.Calls < Q1 - 1.5*IQR | CustServ.Calls > Q3 + 1.5*IQR) %>%
  select(CustServ.Calls)
sort(unique(outliers$CustServ.Calls))
```

Outliers using the IQR method are the customers who made the following number of calls:  
**`r sort(unique(outliers$CustServ.Calls))`**
 
## 4. Transform the day minutes attribute using Z-score standardization.

```{r}
churn$Day.Mins_zscore <- (churn$Day.Mins - mean(churn$Day.Mins)) / sd(churn$Day.Mins) 
head(churn$Day.Mins_zscore)
```

## 5. Work with skewness as follows:  
### a. Calculate the skewness of day minutes.  
```{r}
skew <- 3 * (mean(churn$Day.Mins) - median(churn$Day.Mins)) / sd(churn$Day.Mins)
skew
```

### b. Then calculate the skewness of the Z-score standardized day minutes. Comment.  
```{r}
skew_z <- 3 * (mean(churn$Day.Mins_zscore) - median(churn$Day.Mins_zscore)) / sd(churn$Day.Mins_zscore)
skew_z
```

The skewness remains the same after z-score standardization.

### c. Based on the skewness value, would you consider day minutes to be skewed or nearly perfectly symmetric?  

The skewness of Day.Mins (`r skew`) is close to zero but positive. Therefore, day minutes is nearly perfectly symmetric with a very slight right skewness.

## 6. Construct a normal probability plot of day minutes. Comment on the normality of the data.  

```{r}
ggplot(churn, aes(sample = Day.Mins)) +
  stat_qq(col = "blue") +
  stat_qq_line(col = "red")
```

As the sample matches the normal line very closely, the data is nearly perfectly normal. 

## 7. Work with international minutes as follows:  
### a.  Construct a normal probability plot of international minutes.  

```{r}
ggplot(churn, aes(sample = Intl.Mins)) +
  stat_qq(col = "blue") +
  stat_qq_line(col = "red")
```

The normal probability curve indicates left skewness. This is confirmed from the summary of Intl.Mins where the mean (10.24) is a less than the median (10.3). The skewness calculation returns a negative value (`r 3 * (mean(churn$Intl.Mins) - median(churn$Intl.Mins)) / sd(churn$Intl.Mins)`) and confirms the interpretation of left skewness.

```{r}
summary(churn$Intl.Mins)
skew <- 3 * (mean(churn$Intl.Mins) - median(churn$Intl.Mins)) / sd(churn$Intl.Mins)
skew
```


### b.  What is preventing this variable from being normally distributed.  

```{r}
ggplot(churn) +
  aes(x = "", y = Intl.Mins) +
  geom_boxplot(fill = "blue") +
  scale_y_continuous(n.breaks = 10) +
  theme_bw()

```

```{r}
ggplot(churn, aes(Intl.Mins)) +
  geom_histogram(bins = 40, color = "black", fill = "blue")
```

```{r}
ggplot(churn, aes(Intl.Mins)) +
  geom_histogram(aes(y = ..density..), bins = 40, color = "black", fill = "blue") +
  stat_function(fun = dnorm, args = list(mean(churn$Intl.Mins), sd(churn$Intl.Mins)), color = "red", size = 2)

```

The boxplot shows outlier below 3 and above 17.5. However, the histogram shows around 20 outliers with value 0. This concentration of outliers with 0 value is preventing the data from being normally distributed.

### c.  Construct a flag variable to deal with the situation in (b).  

```{r}
churn <- mutate(churn, Intl.Mins.NZ = ifelse(Intl.Mins == 0, 0, 1))
```

### d.  Construct a normal probability plot of the derived variable nonzero international 	minutes.  

```{r}
ggplot(churn, aes(sample = Intl.Mins.NZ)) +
  stat_qq(col = "blue") +
  stat_qq_line(col = "red")
```

### e.  Comment on the normality of the derived variable.

The derived variable shows the normal probability where its value is 1 and diverges where its value is zero. The zero values are making the distribution left skewed.

```{r}
churn$Intl.Mins.NZ_z <- scale(churn$Intl.Mins.NZ)
skew <- 3 * (mean(churn$Intl.Mins.NZ_z) - median(churn$Intl.Mins.NZ_z)) / sd(churn$Intl.Mins.NZ_z)
skew
```


## 8. Transform the night minutes attribute using Z-score standardization. Using a graph, describe the range of the standardized values.

```{r}
churn$Night.Mins_zscore <- scale(churn$Night.Mins)

ggplot(churn) +
  aes(y = "", x = Night.Mins_zscore) +
  geom_boxplot(fill = "blue") +
  scale_x_continuous(n.breaks = 20) +
  theme_bw()

```

From the boxplot, we can see that 

* the z-score has a median of 0
* Ist quartile = -0.7
* 3rd quartile = 0.7
* the IQR is Q3 - Q1 = 1.4
* the range is from -2.6 to 2.6 (excluding outliers)
* the positive outliers range from 2.8 to 3.8 
* the negative outliers range from -3.5 to -2.6 


